\documentclass{dcthesis}

%This version of the thesis template has been updated for the February 2017 thesis guidelines provided by the School of Graduate and Advanced Studies by David Freund and Daryl DeFord.

%  Some good options are draft and singlespacing, for drafts, and *final*,
%for the final cut, and noheadings, for a printout without headings.  
%You can also use the copyright option to add a copyright.  Note:
%final will enforce a bunch of different options, like oneside, 12pt
%and doublespacing, as well as make the margins correct.   Draft, has
%larger margins and is appropriate for twosided printing.   


%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%    IMPORTANT     %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  Because dvips doesn't know/care about the page size of the dvi file
%  its working on, and because its so important that the margins of
%  your thesis are correct you have to make sure that you are using
%  the command dvi -t letter *thesisnamehere*
%
%  If you are using a terminal this is straightforward, but if you are
%  using a tex editing program it make take a little bit of searching
%  before you figure out how to make this work. 
%  
%  Alternatively, you might consider compiling using pdflatex, which
%  compiles straight to a PDF and doesn't have this problem.  

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Some Defaults
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\committee[F. Jon Kull, Ph.D.]{}{}{}{}{}
\school{Dartmouth College}{Hanover, New Hampshire}
\degree{Doctor of Philosophy}
\field{Quantitative Biomedical Sciences}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Additional Packages (add as desired)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage{amsmath,amssymb,amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{ragged2e}
\usepackage{textcomp}
\usepackage{url}
\usepackage{nameref}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{rotating}
\usepackage[labelfont=bf]{caption}
\usepackage{graphics}
\usepackage{longtable} % for 'longtable' environment
\usepackage{pdflscape}

%\usepackage{mkindex} %Uncomment if you would like to have an index. Compiling with an index takes more work than compiling without one. You will have to look up how to use the index package.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Formatting
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Change or add to as desired. 
%  These two commands make the first enumerations look like (a)
%  And the second level like (i).  
\renewcommand{\labelenumi}{(\alph{enumi})}
\renewcommand{\labelenumii}{(\roman{enumii})}
%  These commands make the section headings Boldface and not all
%  caps. It also removes the chapter numbers  
\renewcommand{\chaptermark}[1]{\markboth{{\sc #1}}{{\sc #1}}}
\renewcommand{\sectionmark}[1]{\markright{{\sc \thesection\ #1}}}
%  These commands have lowercase headings with chapter numbers. 
%\renewcommand{\chaptermark}[1]{markboth{#1}{}}
%\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}} 
		
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Theorem Declarations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A basic set of theorem declarations.  Add or remove as desired. 
\newtheorem{prop}{Proposition}[chapter]
\newtheorem{theorem}[prop]{Theorem}
\newtheorem{lemma}[prop]{Lemma}
\newtheorem{corr}[prop]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[prop]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[prop]{Remark}
\newtheorem{example}[prop]{Example}
\newtheorem*{claim}{Claim}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Indicies
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%This is for an index.  More work is neede for a notation index
%\makeindex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Macros
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Add your math macros here
\newcommand{\overbar}[1]{\mkern 2mu\overline{\mkern-2mu#1\mkern-20mu}\mkern 20mu}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title Page Information
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Your personal info goes here!
\title{Deciphering taxa-function relationships in population-level studies of human gut microbiomes}
\author{Quang P. M. Nguyen}
\date{May 2022}
\field{Quantitative Biomedical Sciences}
\degree{Doctor of Philosophy}
%As an optional arguement to \committee you can specify the dean of graduate studies.
\committee[]{H. Robert Frost, Ph.D.}{Anne G. Hoen, Ph.D.}{Margaret R. Karagas, Ph.D.}{Brock C. Christensen, Ph.D.}{Levi Waldron, Ph.D.}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Front end of thesis
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\frontmatter

\newgeometry{left=1.5in,top=1in,bottom=1in,right=1in}
\maketitle
\restoregeometry

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%NOTE:  Must be less than 350 words.  
\chapter*{Abstract}
%This is so the abstract appears in the ToC
\addcontentsline{toc}{section}{Abstract}
The human gut microbiome is a complex and dynamic ecosystem, featuring a multitude of microbes all interacting with their hosts in an elaborate manner. Even though this exchange is often mediated through microbial metabolic and functional outputs, such as the production of certain metabolites, environmental exposures and host lifestyle are highly influential in shaping the presence of microbial species irrespective of their individual roles. As such, a comprehensive understanding of the microbiome requires researchers to examine the relationship between taxonomic abundance and function simultaneously. Assessing microbial contributions to important ecosystem services can enable identification of robust functions supported by a variety of species, or to identify important keystone taxa that are associated with a disease-causing biochemical pathway. The primary objective of this thesis is to assess different approaches for investigating the taxa-function relationship and evaluate its value in providing unique biological insights. First, we leveraged densely collected multi-omics data from the New Hampshire Birth Cohort Study to identify genus-metabolite pairs that are core to infant gut microbiomes. Second, we developed a novel statistical method that enable integrating taxa-function relationships in epidemiological studies. Third, we assessed microbial phenotypic traits as a potential source for defnining interpretable and human-centric microbiome functions. 

\chapter*{Preface}
\addcontentsline{toc}{section}{Preface}

This thesis would not have been written if it were not for my undergraduate advisor, Dr. Larissa Williams. Even though I had been studying science for while, I was not really introduced to the conduct and methodology of scientific research until I took the advanced molecular biology course at Bates College instructed by Dr. Williams. The methods-focused approach to biology showed me how much I enjoyed the act of doing science (despite some pretty unsavory grades in the standard biology courses). I came to understand that scientific research is an act of love driven by curiosity and excitement. There is nothing else as thrilling as being able to tackle a difficult question armed with a set of tools you know by heart. Dr. Williams' mentorship was the major reason why I applied to graduate school in the first place, which was the first step towards completion of this work.  

I would be remiss to not thank my graduate advisors, Dr. Anne Hoen and Dr. H. Robert Frost, without whom I would have been completely lost. I am amazed at how you are able to tolerate me even after three mental breakdowns (one for each manuscript, like clockwork). I am eternally grateful for your mentorship and guidance. Your patience and dedication to independent research has allowed me to confidently explore a diverse array topics, even if the end result is an eclectic collection of papers that is more akin to looking at a random cabinet at an antique store than anything found at Williams Sonoma. 

This thesis was also supported by the wonderful members of the Hoen and Frost labs. Thank you to Dr. Weston Viles and Dr. Jie Zhou for providing expert statistical help whenever I need them. I am thankful for Dr. Yasmin Kamal, Dr. Modupe Coker, and Courtney Schiebout for all the feedback and enthusiasm on my work at lab meetings. Finally, and most importantly, I would not have survived without Erika Dade's steadfast and expert grasp on all things data, and my lab mate Dr. Rebecca Lebeaux's insightful recommendations. I really appreciate Becky taking the time out of her day to bounce ideas, collaborate, and share our excitement (and the occasional apprehension) for microbiome research. 

I also want to thank my committee members Dr. Margaret Karagas and Dr. Brock Christensen for all of their support and guidance for the past years, who have never said no to anything I asked (even if they are last minute requests). I am also appreciative of Dr. Levi Waldron for agreeing to serve on my dissertation committee.   

I am thankful for all the assistance from researchers within and oustide of Dartmouth. Special thanks to members of the Dartmouth microbiome research group Dr. Juliette Madan, Dr. Modupe Coker, Dr. Hannah Laue, Dr. Thomas Palys, and Yuka Moroishi; as well as my collaborators Dr. Susan Sumner, Dr. Susan McRitche, and Dr. Wimal Pathmasiri from the UNC Nutrition Institute, and Dr. Hilary Morrison from the Marine Biological Laboratory. I am thankful for all the staff and participants of the New Hampshire Birth Cohort Study for their efforts.  

I would like to acknowledge the funding sources that have made this research possible. My work is supported by grants from the NIH (grants R21CA253408, P20GM130454, and R01LM012723) and from the EPA (grants EPA RD-83544201).  

So much of this thesis is also owed to the wonderful QBS community. I want to give thanks to Dr. Diane Gilbert-Diamond, Dr. James O'Malley, Dr. Krissy Griffin, Rosemary White, Shaniqua Jones, and so many others who have helped create a supportive, fun, and wonderful community. Special love for the 62 Sachem crew, Yuka Moroishi and Diana Song (and Keke Song) for 3 years of wonderful co-habitating. Always grateful for my life-long friends Catherine Pollack, Becky Lebeaux and Despina Karalis. I also cannot forget my co-workers at the COVID Tracking Project: Kara Schechtman, Michal Mart, Nicki Camberg, Brandon Park, and Rebecca Glassman, all of whom gave me an amazing community at the darkest of times.  

My final dedications are for my family. I would not have been here at this point without my parents, my aunts, and my cousins. They have been incredibly supportive, and are my biggest cheerleaders. I would also like to thank the Ziegler family, who have allowed me to eat all the soda bread in their house for a whole year. Lastly, my most heartfelt thanks to my partner, Katie Ziegler, for all her support in the past years. I constantly annoy her by asking about the difference between ``genera" and ``genus" (and still getting it wrong), yet she has shown nothing but patience and love. I do not have enough words to express how much you mean to me, and how much your presence have given me strength to move forward.  









%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Table of Contents
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tableofcontents

%Add a list of figures
\listoffigures

%Add a list of tables
\listoftables

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Main Portion of Thesis
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mainmatter

%%%%%%%%%%%%%%%%%%%%%%%%%
%%  YOUR THESIS HERE!  %%
%%%%%%%%%%%%%%%%%%%%%%%%%
\include{chapter1}
\include{chapter2}
\include{chapter3}
\include{chapter4}
\include{chapter5}
%\include{example}
\appendix
\include{appendixA}
\include{appendixB}
\include{appendixC}
\include{appendixD}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Backend of thesis (references and the like)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\backmatter

%Add your bibliography filename and uncomment these lines
\bibliographystyle{amsplain}
\addcontentsline{toc}{chapter}{References}
\bibliography{thesis}
\markboth{{\sffamily\sc Bibliography}}{}


%Uncomment if you want an index
%\printindex

\end{document}